Reproducible Summary Tables with the \pkg{gtsummary} Package

### 2021-04-13 gtsummary_submission.tex
Updates from Overleaf

While other R packages are available to present data and regression model summary tables, such as such as \CRANpkg{skimr}, \CRANpkg{stargazer}, \CRANpkg{finalfit}, and \CRANpkg{tableone}, \pkg{gtsummary} is unique in that it is a one-stop-shop for most types of statistical tables and offers diverse features to customize content of tables to a high degree. 
The default \CRANpkg{gtsummary} table is suitable to be published in a scientific journal with little or no additional formatting.
For example, \CRANpkg{gtsummary} has specific internal algorithms to identify variable data types so the user does not have to specify if a variable should be displayed with categorical or continuous summaries, which yields the summary table with minimal code.

@@

To showcase \pkg{gtsummary} functions, we will use a simulated clinical trial data set containing baseline characteristics of 200 patients who received Drug A or Drug B, as well as the outcomes of tumor response and death.
Each variable in the data frame has been assigned an attribute label with the \pkg{labelled} package \citep{labelled}, e.g. \code{trial \%>\% set\_variable\_labels(age = "Age")} that will be shown in the summary tables. 
These labels are displayed in the \pkg{gtsummary} tables by default, and had labels not been assigned the variable name would have been shown.

@@

% \newpage
\begin{example}
trial %>%
  select(age, grade, trt) %>%
  tbl_summary(by = trt, missing = "no") %>%
  add_overall() %>%
  add_p() %>%
  add_q() %>%
  add_stat_label() %>%
  bold_p(t = 0.10) %>%
  bold_labels() %>%
  modify_header(label ~ "**Variable**") %>% 
  modify_spanning_header(c(stat_1, stat_2) ~ "**Treatment Received**") %>%
  as_gt() %>%
  gt::tab_header(
    title = gt::md("**Table 1. Patient Characteristics**"),
    subtitle = gt::md("_Highly Confidential_")
  ) %>%
  gt::tab_source_note("Data updated June 26, 2015")
\end{example}
\begin{widefigure}[h!]
  \includegraphics[scale=0.49]{custom.png}
  \centering
\end{widefigure}

>>>>

While other R packages are available to present data and regression model summary tables, such as \CRANpkg{skimr}, \CRANpkg{stargazer}, \CRANpkg{finalfit}, and \CRANpkg{tableone}, \pkg{gtsummary} is unique in that it is a one-stop-shop for most types of statistical tables and offers diverse features to customize content of tables to a high degree. 
The default \CRANpkg{gtsummary} table is suitable to be published in a scientific journal with little or no additional formatting.
For example, \CRANpkg{gtsummary} has specific internal algorithms to identify variable data types so the user does not have to specify if a variable should be displayed with categorical or continuous summaries, which yields summary tables with minimal code.

@@

To showcase \pkg{gtsummary} functions, we will use a simulated clinical trial data set containing baseline characteristics of 200 patients who received Drug A or Drug B, as well as the outcomes of tumor response and death.
Each variable in the data frame has been assigned an attribute label with the \pkg{labelled} package \citep{labelled}, e.g. \code{trial \%>\% set\_variable\_labels(age = "Age")} that will be shown in the summary tables. 
These labels are displayed in the \pkg{gtsummary} tables by default, and had labels not been assigned, the variable name would have been shown.

@@

% \newpage
\begin{example}
trial %>%
  select(marker, response, trt) %>%
  tbl_summary(by = trt, missing = "no", 
              statistic = list(marker ~ "{mean} ({sd})")) %>%
  add_overall() %>%
  add_difference() %>%
  add_stat_label() %>%
  bold_labels() %>%
  modify_header(label ~ "**Variable**") %>%
  modify_spanning_header(c(stat_1, stat_2) ~ "**Randomization Assignment**") %>%
  as_gt() %>%
  gt::tab_header(
    title = gt::md("**Table 1. Treatment Differences**"),
    subtitle = gt::md("_Highly Confidential_")
  ) %>%
  gt::tab_source_note("Data updated June 26, 2015")
\end{example}
\begin{widefigure}[h!]
  \includegraphics[scale=0.49]{custom.png}
  \centering
\end{widefigure}
